### 2021-01-12 LaTeX-USENIX/sections/paper.tex
more edits

\textblue{The only other paper similar to ours is TEX~\cite{khalil2019tex}. }

@@

\cm is open source and written in 350 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC). Refer to the availability section at the end of the paper. We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics. Once deployed, the bytecode of \cm is 10812 bytes plus the constructor code (6400 bytes) which is not stored. We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings (\eg a costly loop) that are intentional design choices). Table~\ref{tab:cm_functions} summarizes \cm's primary operations.

@@

In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a price improvement. A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement. For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price from their orders---and it removes any incentive to front-run these profits.

@@

Beyond the cleaning up issues with priority queues, \cm also uses mappings with each market. Traders preload their account with ERC-20 tokens and/or ETH. \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time. However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader). Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}. Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.

@@

\subsection{Token Divisibility and Volumes}

\textblue{Mahsa: Partial Filling: we ran the worst case matching test with random volumes between 1 and 10 on linked list with mapping (which handles maximum pairs of 80 orders with single volumes).  With partial filling, it can clear the book that contains 70 pairs at max (which on average ends up being ~118 trades). SO it is moderately more expensive}

We implemented a very simple market where orders all have the same volume: 1 token. Traders submit multiple orders to increase volume. To extend orders with a volume field, it must first be determined if the token is non-divisible or divisible (and to what precision). In this case, \texttt{closeMarket()} needs to look at multiple bids to fulfill a single ask (and vice-versa) and declare its trading rules on partial fills. We also simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices). A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach is also contingent on the divisibility of tokens. Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price. There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).

@@

As a simple module, \cm is a one-shot market. However it can be extended to re-open with a clean order book after \texttt{closeMarket()} is run. Modifiers can enforce when the market operates openly (collecting orders) and when close can be run. In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or gasUsed in Ethereum).

If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market every block. Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is next) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation. Since price improvements are paid to the miners, the miner is incentivized to run \texttt{closeMarket()} last to make the most profit. Perhaps in a world where these markets became immensely popular, miners would actually do this, but as it stands, miners do not generally search for the transaction ordering that nets them the most profit.

A close alternative is to allow markets to open and close on different blocks. Specifically, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.

The final issue is who invokes \texttt{closeMarket()} every other block? There are actually two issues here: the issue of scheduling the function call and the issue of paying for it. For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock.\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.

@@

It is unlikely that a mining software will become aware of specific DApps, but miners are paid all price improvements in the market and so it is possible that running \texttt{closeMarket()} would pay for itself. However we consider two other (more realistic) scenarios. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until the order book is empty). Once the time window for submitting orders is past, a new market is created (without settling the previous market). Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market. This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).

The second solution is to levy a carefully computed fee against the traders for every new order they submit. These fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty. This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However an interested third party (such as the token issuer for a given market) might bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}).

%= = = = = =  = =  =  Rollups=  = = = = = = = = =%

@@

@@

Imagine you have just launched a standard token on Ethereum. Now want your holders to be able to trade it. While the barrier to entry for exchange services is low, it still exists. For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request. For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens. For rollups, you will have to host your own servers. By contrast to all of these, with an on-chain orderbook, you just deploy the code alongside your token and trading is immediately supported. Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token. With future improvements to blockchain scalability, it could become the defacto trading method.

@@

\subsubsection*{Availability} 
The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted). We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0xffcaae2a77254b4cd72356b27377408ab31155b4}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.offchainlabs.com/#/tx/0x500bee14a58d6d602a697cb858b78b5f071320a1d544c44fbea00048124b1ea8}{[explorer.offchainlabs.com]} (both links are anonymized).

>>>>

The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}. TEX is also an implementation of an orderbook however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain orderbook is. It is similar to our variant with roll-ups however it uses a different architecture where users interact directly with the off-chain component (a regulatory hook). The other overlap is the focus on resisting front-running attacks. In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed. One solution is to provide confidentiality over the content of orders which is the approach taken by TEX. The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders. The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third party service~\cite{Kla20} (a regulatory hook). These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A. Juels. \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}). The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.

% https://eprint.iacr.org/2020/269.pdf
% Wendy, the Good Little Fairness Widget – Achieving Order Fairness for Blockchains

@@

\cm is open source and written in 350 lines (SLOC) of Solidity plus the priority queue (\eg a heap with dynamic array is 282 SLOC). Refer to the availability section at the end of the paper. We tested it with the Mocha testing framework using Truffle on Ganache-CLI to obtain our performance metrics. Once deployed, the bytecode of \cm is 10812 bytes plus the constructor code (6400 bytes) which is not stored. We cross-checked for vulnerabilities with \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}\footnote{https://tool.smartdec.net} (it only fails some `informational' warnings that are intentional design choices---\eg a costly loop). Table~\ref{tab:cm_functions} summarizes \cm's primary operations.

@@

In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement}. A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement. For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.

@@

Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market. Traders preload their account with ERC-20 tokens and/or ETH. \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time. However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader). Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}. Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.

@@

\subsection{Token Divisibility and Ties}

When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order. In \cm, tokens are assumed to be divisible. We simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices). A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work. Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price. There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).

@@

As a simple base class, \cm is a one-shot market. However it can be extended to re-open with a clean order book after \texttt{closeMarket()} is run. Modifiers can enforce when the market operates openly (collecting orders) and when close can be run. In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or gasUsed in Ethereum).

If the call market runs as a DApp on Ethereum, it seems difficult to open and close the market every block. Someone needs to call the \texttt{closeMarket()} for every block (we return to who this is next) but the market will only work as intended if miners execute this function after every \texttt{submitBid()} and \texttt{submitAsk()} invocation. Since price improvements are paid to the miners, the miner is actually incentivized to run \texttt{closeMarket()} last to make the most profit. This pattern is called miner extractable value (MEV)~\cite{daian2019flash} and is usually considered in the context of attacks. However in our case, MEV is a feature. Efficient algorithms for miners to automatically find MEV opportunities is an open research problem.

A close alternative is to allow markets to open and close on different blocks. In this alternative, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.

The final issue is who invokes \texttt{closeMarket()} every other block? There are actually two issues here: the issue of scheduling the function call and the issue of paying for it. For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.

@@

As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself. However we consider two other scenarios that do not assume miners can automatically find MEV opportunities. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the orderbook from locking up because the number of orders exceeds the gas limit to process them).  Once the time window for submitting orders is past, a new market is created (without settling the previous market). Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market. This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).

The second solution is to levy a carefully computed fee against the traders for every new order they submit. These fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty. This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
%= = = = = =  = =  =  Rollups=  = = = = = = = = =%

@@

\textblue{Re-align this section}

@@

Imagine you have just launched a standard token on Ethereum. Now want your holders to be able to trade it. While the barrier to entry for exchange services is low, it still exists. For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request. For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens. For rollups, you will have to host your own servers. By contrast to all of these, with an on-chain orderbook, you just deploy the code alongside your token and trading is immediately supported. This should concern regulators. Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token. With future improvements to blockchain scalability, it could become the defacto trading method.

It may seem paradoxical or unethical to build for regulators exactly what they worry about, however we agreed that it was too difficult to answer our research questions without actual implementation and experimentation. \cm is proof of concept code that implements only enough to understand the feasibilty of on-chain trading and we release the code for reproducibility. However it is not production code, it is unpolished, it has no UI, and we have no intention of promoting it for adoption. Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, roll-up servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.

@@

\subsubsection*{Availability} 
The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted). We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.arbitrum.io/#/tx/0x1828d7eb6a7a9b9ec479f07e8149c6172bb89a101571963b5cf690132bdf009b}{[explorer.offchainlabs.com]} (both links are anonymized).
